### 2017-05-02 article/main.tex
init article

\documentclass[sigconf]{acmart}

\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers

\usepackage[utf8]{inputenc}	
\usepackage[T1]{fontenc}

\usepackage{multirow}
\usepackage{booktabs} 
\usepackage{colortbl}
\usepackage{todonotes}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{pdfpages}
\usepackage{balance}
\usepackage{mdframed}
\usepackage{hyperref}

\usepackage[labelformat=simple]{subcaption}
\renewcommand\thesubfigure{(\alph{subfigure})}
\definecolor{Gray}{gray}{0.9}

\setcopyright{rightsretained}

\begin{document}

\title{Airbnb - New York’s Analysis}

\author{Jackson A. Prado Lima}
\affiliation{
	\institution{Department of Computer Science, Federal University of Paran\'{a}}
	\city{ CP:19081, CEP: 81531-980, Curitiba} 
	\state{Paran\'{a}}
	\country{Brazil}
}
\email{japlima@inf.ufpr.br}

\renewcommand{\shortauthors}{J. A. Prado Lima}
\renewcommand{\shorttitle}{Airbnb - New York’s Analysis}

\begin{comment}
\begin{abstract}

The selection of products for the variability testing of Feature Models (FMs) is a complex task impacted by many factors. To solve this problem, Multi-Objective and Evolutionary Algorithms (MOEAs) have been successfully used in the field known as Search-Based Software Engineering (SBSE). However, the design of a search-based approach is not an easy task for the software engineer, who can find some difficulties such as: the choice and configuration of the best MOEAs, the choice of the best search operators to be implemented, and so on. In addition to this, existing approaches are dependent on the problem domain and do not allow reuse. In this way the use of Hyper-Heuristic (HH) can help to obtain more generic and reusable search-based approaches, and because of this is considered a trend in the SBSE field. Following this trend and to contribute to reduce the software engineer's efforts, this work explores the use of a hyper-heuristic for automatically generation of MOEAs to select test products from the FM, considering three factors: pairwise coverage, mutation score and cost, given by the number of products. The HH is based on a grammar that represents the elements, parameters and components of existing MOEAs and implements evolutionary operators, such as crossover and mutation, suitable for selection problems. In this way, it can be reused for other similar software engineering problems. Evaluation results show that the proposed approach obtains results that are better or statistically equivalent than similar approaches found in the literature.
\end{abstract}

\keywords{Software Product Line Testing, Search-Based Software Engineering, Hyper-Heuristics} 
\end{comment}

\begin{abstract}
	Airbnb is an outstanding hosting service used worldwide and provides information to its users in a simple and efficient manner, although this information is limited only to listings of its products. In this work, an analysis is made taking into account if incidents and cultural organizations influence the prices practiced in Airbnb. Besides, the prediction of new prices is carried out that the user can come to inform taking into account information of the current listings. The price forecast has some advantages when advising the user: on the price practiced (is too large or small), the mode of advertisement, or even on the investment decisions of the market analysis. To help in this task, the present work performs an analysis using graphs, maps and different types of machine learning.
\end{abstract}

%\keywords{BigData, Machine Learning, Airbnb}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-0.5cm}
\section{Introduction}

Airbnb was founded in August of 2008 and based in San Francisco, California. Airbnb is an online marketplace and hospitality service, enabling people to lease or rent short-term lodging including vacation rentals, apartment rentals, homestays, hostel beds, or hotel rooms.

The company does not own any lodging; it is merely a broker and receives percentage service fees (commissions) from both guests and hosts in conjunction with every booking. It has over 3,000,000 lodging listings in 65,000 cities and 191 countries, and the host sets the cost of accommodation. Like all hospitality services, Airbnb is a form of collaborative consumption and sharing. Airbnb has two million rooms available - nearly three times more than that of the largest hotel chain in the world.

How can we predict if a guest will continue booking rooms through Airbnb, and how can we predict if a host will continue listing out their property on Airbnb? Unlike traditional hotels, Airbnb relies on one group of its customers (hosts) to generate the supply of rooms for its guests. Thus, predicting customer loyalty, both on the host side and guest side, is arguably more important to Airbnb than to traditional hotels. In this paper, we try and capture this loyalty to Airbnb.

The data reveals that guests who stay with highly rated hosts are far more likely to return to Airbnb. For hosts, the best predictors of whether or not they will
continue to list through Airbnb is the recency and frequency of their listing.

%A proposta deste trabalho é utilizar três fontes de dados distintas na ferramenta de processamento de dados distribuídos Apache Spark e em seguida executar um algoritmo de aprendizado de máquina para aprender algo a partir dos dados que estão sendo utilizados.

%Para cumprir com as exigências do trabalho, foram selecionadas três bases de dados do governo brasileiro relativo às obras do PAC. O PAC, acrônimo de Programa de Aceleração do Crescimento, foi proposto pelo governo brasileiro em 2007 como um plano estratégico de resgate do planejamento e de retomada dos investimentos em setores estruturantes do país.

%O PAC possibilitou obras em diversos setores como saúde, educação, economia, turismo entre outras. Como o PAC abrange uma quantidade bastante grande de setores de investimento, há diversas possibilidades de pesquisa. Portanto foi escolhido um subconjunto dos dados para que os resultados fossem mais precisos. Desta forma, foi escolhido um setor de investimento, no caso o turismo. Esta escolha teve como base os dois grandes eventos esportivo de 2014 e 2016 (Copa do mundo de futebol e Olimpíadas respectivamente) e as bases de dados coletadas são de 2015, pareceu interessante investigar as obras do PAC que possuem cunho turístico.

%A seguir, na Seção \ref{Seção:Dados Utilizados}, será discutido um pouco mais sobre as bases de dados, os formatos disponíveis e o processamento realizado para possibilitar a utilização de aprendizado de máquina. Na Seção \ref{Seção:Investigando a base de dados} serão expostos e discutidos alguns resultados obtidos após a análise feita na base de dados utilizando apenas o Apache Spark, sem o uso de aprendizado de máquina. Esta análise tem como objetivo entender um pouco mais sobre os dados que foram utilizados neste trabalho. Em seguida, na Seção \ref{Seção:Predizendo dados} será proposta uma pergunta de pesquisa para ser respondida com o uso de aprendizagem de máquina, o experimento será explicado e os resultados expostos e discutidos. Já encaminhando para o fim do trabalho, na Seção \ref{Seção:Problemas encontrados} serão apresentados os problemas encontrados durante a execução deste trabalho. Por fim, na Seção \ref{Seção:Conclusão} serão relatadas as conclusões obtidas com este trabalho, em conjunto com os possíveis trabalhos futuros.

The paper is organized as follows. Section~\ref{sec:experiment_description} describes how the experimental evaluation was conducted. Section~\ref{sec:results} presents and analyses the results obtained. Finally, Section~\ref{sec:conclusion} concludes the paper and discusses the future work.

\vspace{-0.2cm}
\section{Experiment Description}
\label{sec:experiment_description}

The hypothesis of this work is that our approach is capable to recommend a local (district/borough) or a price to a user. To evaluate this, we consider uses maps, charts and machine learning.

According to our goals the experiment was guided by the following research question: \textbf{RQ:} ``How the incidents and cultural organizations impact on listing price?''.

To answer the RQ we conducted the evaluation in three phases: (i) Charts; (ii) Maps; and (iii) Machine Learning. In the first phase, we analyses the data distribution. In the second phase, we understand the impact of different factors using maps. In the last phase, we applies machine learning to predict some data.

From the main question we divided in other questions to understand different points:

\begin{itemize}
	\item \textbf{RQ1}: How the the cultural organizations impact on listing price?
	\item \textbf{RQ2}: How the the incidents impact on listing price?
	\item \textbf{RQ3}: How can we use average value rating, average location rating, etc. in the data?	
\end{itemize}

\vspace{-0.2cm}
\subsection{Target Data}
\label{sec:experiment_description:target_data}

The investigation focused on four dataset collected in open data sites. These dataset are as follows: 1) Listings, a dataset that is a Airbnb snapshot of 02 April, 2017; 2) Incidents, contains all incidents from New York for the year 2016; 3) Cultural Organizations, contains all cultural organizations from New York in 2017; and 4) NYC Borough, contains informations about boundaries of boroughs (districts). Further information about these datasets are available in the Table~\ref{tab:datasets}.

\begin{table*}[!htpb]
	\fontsize{9pt}{9pt}\selectfont
	\centering
	\caption{Characteristics of the data sets used in the experiment.}
	\label{tab:datasets}
	\begin{tabular}{ccp{10cm}cc}
		\toprule
		\textbf{\#} &              \textbf{Dataset}               & \textbf{Description}                                                                                                                          & \textbf{Size} & \textbf{Download} \\ \midrule
		     1      &         Listings~\cite{base:airbnb}         & Detailed listings data, including various attributes (features) of each listing such as number of bedrooms, bathrooms, location, etc.         &    153,7MB    &        csv        \\ \midrule
		     2      &       Incidents~\cite{base:incidents}       & All valid felony, misdemeanor, and violation crimes reported to the New York City Police Department (NYPD) for all complete quarters in 2016. &    124,2MB    &        csv        \\ \midrule
		     3      & Cultural Organizations~\cite{base:cultural} & Listing of all Cultural Organizations in the Department of Cultural Affairs directory.                                                        &    333,3kB    &        csv        \\ \midrule
		     4      &       NYC Borough~\cite{base:borough}       & Polygon boundaries of boroughs (water areas excluded).                                                                                        &    400,5kB    &      GeoJson      \\ \bottomrule
	\end{tabular}
\end{table*}

\vspace{-0.2cm}
\subsection{Settings}

In this step was used three different approaches to read the data (csv files): (i) SqlContext with databricks; (ii) parquet; and (iii) pandas. After, it was create a unique dataframe with the necessary informations. To help in the analsys, the Cultural Organizations and Incidents dataset received a score a they are like a column unique in the new dataframe. How we have 5 districts in New York, and to be easy, the Cultural Organizations and Incidents dataset were grouped and ranked in relation to the order (1-5), where 1 is the work and 5 the best. In this case, the datasets were ordered by the number in each district, ascendant for cultural organizations and descendant for the incidents.

\section{Results and Analysis}
\label{sec:results}

\subsection{RQ1 - Comparing}

\subsection{RQ2 - UCB}

\subsection{Threats To Validity}
\label{sec:results:threats}

\section{Concluding Remarks}
\label{sec:conclusion}

\balance
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}

\begin{comment}
\subsection{Analyzing the data}

The objective of this step is to know the data and improve our understanding of the problem. The dataset contains 37043 rows, where each row represents a listing on the Airbnb and each column contains some information about them. Addictionally, ratings were created for the cultural and incident indexes, respectivally the columns: cultural\_organizations and nypd\_complaint (incidents). The columns are:

\begin{itemize}
\item \textbf{id}: listing id
\item \textbf{latitude and longitude}: latitude and longitude of the listing
\item \textbf{is\_location\_exact}: a boolean thats confirm the localization
\item \textbf{host\_id}: the host id
\item \textbf{host\_name}: the host name
\item \textbf{host\_response\_time}: the host response time 
\item \textbf{host\_response\_rate}: the host response rate 
\item \textbf{host\_is\_superhost}: if the host is superhost
\item \textbf{host\_listings\_count}: the host listings count
\item \textbf{host\_total\_listings\_count}: the host total listings count
\item \textbf{host\_identity\_verified}: if the host was verified
\item \textbf{neighbourhood}: the listings neibourhood
\item \textbf{district}: the listings district
\item \textbf{property\_type}: These options are pretty straightforward. To avoid any confusion, Airbnb added a brief description of each property (home) type that appears when your mouse hovers over. Select the option that best describes your place. Keep in mind that the drop-down menu to the right expands your list of choices pretty significantly, including everything from loft, to castle, to tent.
\item \textbf{room\_type}: all listings are grouped into the following three room types: \textit{Shared rooms}, \textit{Private rooms}, \textit{Entire homes / apartments}. 
\begin{itemize}
\item \textbf{Shared rooms}: are for when you'd like a comfy, communal experience, and don't mind sharing a space with others. When you book a shared room, you'll be sharing your bedroom and the entire space with other people. These rooms work best for the flexible traveler looking for new friends and a budget-friendly stay.
\item \textbf{Private rooms}: are great for when you prefer a little privacy, but still value a local connection. When you book a private room, you'll have a bedroom to yourself, but will share some spaces with others. With a private room, you'll be able to wake up to greet your new friends in the kitchen and have the freedom to bid them adieu at bedtime.
\item \textbf{Entire homes/apartments}: are best if you're seeking a home away from home with complete privacy and the freedom to cook breakfast in your pajamas. With an entire home/apartment, you'll have the whole space to yourself. You can be your own host, make your own dinner, and remember to treat your listing with the respect and courtesy you would at your own home.
\end{itemize}
\item \textbf{accommodates}: This allows you to select the maximum number of people that can comfortably fit in your place. It’s important to understand that capacity is not limited to bed space: you will have the opportunity to indicate the number of available beds in the subsequent steps (given you selected the “Entire home/apt” room type). For now, calculate how many people you can accommodate if each has his or her own bed, sofa bed, or inflatable mattress, provided that the sleeping arrangement is as comfortable as you would expect if you were the guest yourself. Finally, select the appropriate number from the drop-down list given.	
\item \textbf{bathrooms}: the number of bathrooms
\item \textbf{bedrooms}: the number of bedrooms
\item \textbf{beds}: the number of beds
\item \textbf{bed\_type}: the bed type
\item \textbf{price}: the price
\item \textbf{weekly\_price}: the weekly price
\item \textbf{monthly\_price}: the monthly price
\item \textbf{security\_deposit}: the security deposit
\item \textbf{cleaning\_fee}: the cleaning fee
\item \textbf{guests\_included}: the guests included
\item \textbf{extra\_people}: the price for each extra people
\item \textbf{minimum\_nights}: the minimum nights
\item \textbf{maximum\_nights}: the maximum nights
\item \textbf{availability\_30}: the availability in 30 days
\item \textbf{availability\_60}: the availability in 60 days
\item \textbf{availability\_90}: the availability in 90 days
\item \textbf{availability\_365}: the availability in 365 days
\item \textbf{number\_of\_reviews}: the number of reviews
\item \textbf{review\_scores\_rating}: the review scores rating
\item \textbf{review\_scores\_accuracy}: the review scores accuracy
\item \textbf{review\_scores\_cleanliness}: the review scores cleanliness
\item \textbf{review\_scores\_checkin}: the review scores checkin
\item \textbf{review\_scores\_communication}: the review scores communication
\item \textbf{review\_scores\_location}: the review scores location
\item \textbf{review\_scores\_value}: the review scores value
\item \textbf{review\_per\_month}: the review per month
\item \textbf{instant\_bookable}: if is instant bookable
\item \textbf{cancellation\_policy}: the cancellation policy
\item \textbf{require\_guest\_profile\_picture}: if required guest profile picture
\item \textbf{require\_guest\_phone\_verification}: if require guest phone verification
\item \textbf{calculated\_host\_listings\_count}: the calculated host listings count
\item \textbf{cultural\_organizations}: the score of the district in relation the number of cultural organization between 1 (worst) and 5 (best). We have 5 districts, so they are ordered and the score was make in relation the order.
\item \textbf{incidents}: the score of the district in relation the incidents between 1 (worst) and 5 (best). We have 5 districts, so they are ordered and the score was make in relation the order.
\end{itemize}
\end{comment}

### 2017-05-03 article/main.tex
update project

@@
 \renewcommand{\shorttitle}{Airbnb - New York’s Analysis}
-
-\begin{comment}
-\begin{abstract}
-
-The selection of products for the variability testing of Feature Models (FMs) is a complex task impacted by many factors.
-To solve this problem, Multi-Objective and Evolutionary Algorithms (MOEAs) have been successfully used in the field known as Search-Based Software Engineering (SBSE).
-However, the design of a search-based approach is not an easy task for the software engineer, who can find some difficulties such as: the choice and configuration of the best MOEAs, the choice of the best search operators to be implemented, and so on.
-In addition to this, existing approaches are dependent on the problem domain and do not allow reuse.
-In this way the use of Hyper-Heuristic (HH) can help to obtain more generic and reusable search-based approaches, and because of this is considered a trend in the SBSE field.
-Following this trend and to contribute to reduce the software engineer's efforts, this work explores the use of a hyper-heuristic for automatically generation of MOEAs to select test products from the FM, considering three factors: pairwise coverage, mutation score and cost, given by the number of products.
-The HH is based on a grammar that represents the elements, parameters and components of existing MOEAs and implements evolutionary operators, such as crossover and mutation, suitable for selection problems.
-In this way, it can be reused for other similar software engineering problems.
-Evaluation results show that the proposed approach obtains results that are better or statistically equivalent than similar approaches found in the literature.
-\end{abstract}
-
-\keywords{Software Product Line Testing, Search-Based Software Engineering, Hyper-Heuristics} 
-\end{comment}
 
@@
 In this case, the datasets were ordered by the number in each district, ascendant for cultural organizations and descendant for the incidents.
+In the end, we have a unique dataset with 37043 rows.
 
@@
 \label{sec:results}
+
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=\linewidth]{images/price_per_district}
+	\caption{Mean Price per District}
+	\label{fig:casPf}
+\end{figure}
+
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=\linewidth]{images/cultural_organizations_per_district}
+	\caption{Number of Cultural Organizations per District}
+	\label{fig:eshopPf}
+\end{figure}
+
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=\linewidth]{images/incidents_per_district}
+	\caption{Number of Incidents per District}
+	\label{fig:jamesPf}
+\end{figure}
+
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=\linewidth]{images/pairwise_relations_principal_features}
+	\caption{}
+	\label{fig:pairwiserelationsprincipalfeatures}
+\end{figure}
 
@@
 \end{document}
-
-\begin{comment}
-\subsection{Analyzing the data}
-
-The objective of this step is to know the data and improve our understanding of the problem.
-The dataset contains 37043 rows, where each row represents a listing on the Airbnb and each column contains some information about them.
-Addictionally, ratings were created for the cultural and incident indexes, respectivally the columns: cultural\_organizations and nypd\_complaint (incidents).
-The columns are:
-
-\begin{itemize}
-\item \textbf{id}: listing id
-\item \textbf{latitude and longitude}: latitude and longitude of the listing
-\item \textbf{is\_location\_exact}: a boolean thats confirm the localization
-\item \textbf{host\_id}: the host id
-\item \textbf{host\_name}: the host name
-\item \textbf{host\_response\_time}: the host response time 
-\item \textbf{host\_response\_rate}: the host response rate 
-\item \textbf{host\_is\_superhost}: if the host is superhost
-\item \textbf{host\_listings\_count}: the host listings count
-\item \textbf{host\_total\_listings\_count}: the host total listings count
-\item \textbf{host\_identity\_verified}: if the host was verified
-\item \textbf{neighbourhood}: the listings neibourhood
-\item \textbf{district}: the listings district
-\item \textbf{property\_type}: These options are pretty straightforward.
-To avoid any confusion, Airbnb added a brief description of each property (home) type that appears when your mouse hovers over.
-Select the option that best describes your place.
-Keep in mind that the drop-down menu to the right expands your list of choices pretty significantly, including everything from loft, to castle, to tent.
-\item \textbf{room\_type}: all listings are grouped into the following three room types: \textit{Shared rooms}, \textit{Private rooms}, \textit{Entire homes / apartments}. 
-\begin{itemize}
-\item \textbf{Shared rooms}: are for when you'd like a comfy, communal experience, and don't mind sharing a space with others.
-When you book a shared room, you'll be sharing your bedroom and the entire space with other people.
-These rooms work best for the flexible traveler looking for new friends and a budget-friendly stay.
-\item \textbf{Private rooms}: are great for when you prefer a little privacy, but still value a local connection.
-When you book a private room, you'll have a bedroom to yourself, but will share some spaces with others.
-With a private room, you'll be able to wake up to greet your new friends in the kitchen and have the freedom to bid them adieu at bedtime.
-\item \textbf{Entire homes/apartments}: are best if you're seeking a home away from home with complete privacy and the freedom to cook breakfast in your pajamas.
-With an entire home/apartment, you'll have the whole space to yourself.
-You can be your own host, make your own dinner, and remember to treat your listing with the respect and courtesy you would at your own home.
-\end{itemize}
-\item \textbf{accommodates}: This allows you to select the maximum number of people that can comfortably fit in your place.
-It’s important to understand that capacity is not limited to bed space: you will have the opportunity to indicate the number of available beds in the subsequent steps (given you selected the “Entire home/apt” room type).
-For now, calculate how many people you can accommodate if each has his or her own bed, sofa bed, or inflatable mattress, provided that the sleeping arrangement is as comfortable as you would expect if you were the guest yourself.
-Finally, select the appropriate number from the drop-down list given.
-\item \textbf{bathrooms}: the number of bathrooms
-\item \textbf{bedrooms}: the number of bedrooms
-\item \textbf{beds}: the number of beds
-\item \textbf{bed\_type}: the bed type
-\item \textbf{price}: the price
-\item \textbf{weekly\_price}: the weekly price
-\item \textbf{monthly\_price}: the monthly price
-\item \textbf{security\_deposit}: the security deposit
-\item \textbf{cleaning\_fee}: the cleaning fee
-\item \textbf{guests\_included}: the guests included
-\item \textbf{extra\_people}: the price for each extra people
-\item \textbf{minimum\_nights}: the minimum nights
-\item \textbf{maximum\_nights}: the maximum nights
-\item \textbf{availability\_30}: the availability in 30 days
-\item \textbf{availability\_60}: the availability in 60 days
-\item \textbf{availability\_90}: the availability in 90 days
-\item \textbf{availability\_365}: the availability in 365 days
-\item \textbf{number\_of\_reviews}: the number of reviews
-\item \textbf{review\_scores\_rating}: the review scores rating
-\item \textbf{review\_scores\_accuracy}: the review scores accuracy
-\item \textbf{review\_scores\_cleanliness}: the review scores cleanliness
-\item \textbf{review\_scores\_checkin}: the review scores checkin
-\item \textbf{review\_scores\_communication}: the review scores communication
-\item \textbf{review\_scores\_location}: the review scores location
-\item \textbf{review\_scores\_value}: the review scores value
-\item \textbf{review\_per\_month}: the review per month
-\item \textbf{instant\_bookable}: if is instant bookable
-\item \textbf{cancellation\_policy}: the cancellation policy
-\item \textbf{require\_guest\_profile\_picture}: if required guest profile picture
-\item \textbf{require\_guest\_phone\_verification}: if require guest phone verification
-\item \textbf{calculated\_host\_listings\_count}: the calculated host listings count
-\item \textbf{cultural\_organizations}: the score of the district in relation the number of cultural organization between 1 (worst) and 5 (best).
-We have 5 districts, so they are ordered and the score was make in relation the order.
-\item \textbf{incidents}: the score of the district in relation the incidents between 1 (worst) and 5 (best). We have 5 districts, so they are ordered and the score was make in relation the order.
-\end{itemize}
-\end{comment}

### 2017-05-03 article/main.tex
ending write

@@
 To help in this task, the present work performs an analysis using graphs, maps and different types of machine learning.
+The data reveals that Queens district has the more adequate trade-off among price, cultural organization, and incidents as well as the accommodates diversity.
+Besides, cultural organization has a high influence in to predict price.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{-0.5cm}
+%\vspace{-0.2cm}
 \section{Introduction}
@@
 
-The company does not own any lodging; it is merely a broker and receives percentage service fees (commissions) from both guests and hosts in conjunction with every booking.
+%The company does not own any lodging; it is merely a broker and receives percentage service fees (commissions) from both guests and hosts in conjunction with every booking.
 It has over 3,000,000 lodging listings in 65,000 cities and 191 countries, and the host sets the cost of accommodation.
@@
 
-How can we predict if a guest will continue booking rooms through Airbnb, and how can we predict if a host will continue listing out their property on Airbnb?
-Unlike traditional hotels, Airbnb relies on one group of its customers (hosts) to generate the supply of rooms for its guests.
-Thus, predicting customer loyalty, both on the host side and guest side, is arguably more important to Airbnb than to traditional hotels.
-In this paper, we try and capture this loyalty to Airbnb.
-
-The data reveals that guests who stay with highly rated hosts are far more likely to return to Airbnb. For hosts, the best predictors of whether or not they will
-continue to list through Airbnb is the recency and frequency of their listing.
-
-%A proposta deste trabalho é utilizar três fontes de dados distintas na ferramenta de processamento de dados distribuídos Apache Spark e em seguida executar um algoritmo de aprendizado de máquina para aprender algo a partir dos dados que estão sendo utilizados.
-
-%Para cumprir com as exigências do trabalho, foram selecionadas três bases de dados do governo brasileiro relativo às obras do PAC.
-O PAC, acrônimo de Programa de Aceleração do Crescimento, foi proposto pelo governo brasileiro em 2007 como um plano estratégico de resgate do planejamento e de retomada dos investimentos em setores estruturantes do país.
-
-%O PAC possibilitou obras em diversos setores como saúde, educação, economia, turismo entre outras.
-Como o PAC abrange uma quantidade bastante grande de setores de investimento, há diversas possibilidades de pesquisa.
-Portanto foi escolhido um subconjunto dos dados para que os resultados fossem mais precisos.
-Desta forma, foi escolhido um setor de investimento, no caso o turismo.
-Esta escolha teve como base os dois grandes eventos esportivo de 2014 e 2016 (Copa do mundo de futebol e Olimpíadas respectivamente) e as bases de dados coletadas são de 2015, pareceu interessante investigar as obras do PAC que possuem cunho turístico.
-
-%A seguir, na Seção \ref{Seção:Dados Utilizados}, será discutido um pouco mais sobre as bases de dados, os formatos disponíveis e o processamento realizado para possibilitar a utilização de aprendizado de máquina.
-Na Seção \ref{Seção:Investigando a base de dados} serão expostos e discutidos alguns resultados obtidos após a análise feita na base de dados utilizando apenas o Apache Spark, sem o uso de aprendizado de máquina.
-Esta análise tem como objetivo entender um pouco mais sobre os dados que foram utilizados neste trabalho.
-Em seguida, na Seção \ref{Seção:Predizendo dados} será proposta uma pergunta de pesquisa para ser respondida com o uso de aprendizagem de máquina, o experimento será explicado e os resultados expostos e discutidos.
-Já encaminhando para o fim do trabalho, na Seção \ref{Seção:Problemas encontrados} serão apresentados os problemas encontrados durante a execução deste trabalho.
-Por fim, na Seção \ref{Seção:Conclusão} serão relatadas as conclusões obtidas com este trabalho, em conjunto com os possíveis trabalhos futuros.
+Airbnb has help a lot of people, but how can we predict a price or if the cultural organizations and incidents impacts on listing price?
+In some moments, the guests want to a local cheap or more attractive considering local events to appreciate.
+Thus, predicting a cheap and safe local is arguably important.
+In this paper, we try and capture this characteristic using maps, charts and machine learning to help the guest in the chose.
 
@@
 
-\vspace{-0.2cm}
+%\vspace{-0.2cm}
 \section{Experiment Description}
@@
 
-The hypothesis of this work is that our approach is capable to recommend a local (district/borough) or a price to a user. To evaluate this, we consider uses maps, charts and machine learning.
+The hypothesis of this work\footnote{The project is available at https://github.com/jacksonpradolima/airbnb-ny-analysis} is that our approach is capable to recommend a cheap and safe local (district/borough) as well as consider the influence of these aspect in to predict listing price.
+To evaluate this, we consider uses maps, charts and machine learning.
 
-According to our goals the experiment was guided by the following research question: \textbf{RQ:} ``How the incidents and cultural organizations impact on listing price?''.
+According to our goals the experiment was guided by the following researches questions: \textbf{RQ1:} ``How the incidents and cultural organizations impact on listing price?'' and \textbf{RQ2:} ``How the incidents and cultural organizations impact on regression model to predict the listing price?''.
 
-To answer the RQ we conducted the evaluation in three phases: (i) Charts; (ii) Maps; and (iii) Machine Learning.
-In the first phase, we analyses the data distribution.
-In the second phase, we understand the impact of different factors using maps.
-In the last phase, we applies machine learning to predict some data.
+To answer the RQ1 we compared the result shows on maps, a collinearity matrix among the features, and how the accommodates are distributed.
+To answer the RQ2 we used a machine learning with 7 regression models and the results were compared using Median Absolute Error.
 
-From the main question we divided in other questions to understand different points:
-
-\begin{itemize}
-	\item \textbf{RQ1}: How the the cultural organizations impact on listing price?
-	\item \textbf{RQ2}: How the the incidents impact on listing price?
-	\item \textbf{RQ3}: How can we use average value rating, average location rating, etc. in the data?	
-\end{itemize}
-
-\vspace{-0.2cm}
+%\vspace{-0.2cm}
 \subsection{Target Data}
@@
 
-\begin{table*}[!htpb]
-	\fontsize{9pt}{9pt}\selectfont
+%\vspace{-0.2cm}
+\begin{table}[!htpb]
+	\fontsize{7pt}{7pt}\selectfont
 	\centering
-	\caption{Characteristics of the data sets used in the experiment.}
+	\caption{Data sets used in the experiment.}
 	\label{tab:datasets}
-	\begin{tabular}{ccp{10cm}cc}
+	\begin{tabular}{cp{3.5cm}cc}
 		\toprule
-		\textbf{\#} &              \textbf{Dataset}               & \textbf{Description}                                                                                                                          & \textbf{Size} & \textbf{Download} \\ \midrule
-		     1      &         Listings~\cite{base:airbnb}         & Detailed listings data, including various attributes (features) of each listing such as number of bedrooms, bathrooms, location, etc.
+		         \textbf{Dataset}          & \textbf{Description}                                                                                                                          & \textbf{Size} & \textbf{Download} \\ \midrule
+		   Listings~\cite{base:airbnb}     & Detailed listings data, including various attributes (features) of each listing such as number of bedrooms, bathrooms, location, etc.
 &    153,7MB    &        csv        \\ \midrule
-		     2      &       Incidents~\cite{base:incidents}       & All valid felony, misdemeanor, and violation crimes reported to the New York City Police Department (NYPD) for all complete quarters in 2016.
+		 Incidents~\cite{base:incidents}   & All valid felony, misdemeanor, and violation crimes reported to the New York City Police Department (NYPD) for all complete quarters in 2016.
 &    124,2MB    &        csv        \\ \midrule
-		     3      & Cultural Organizations~\cite{base:cultural} & Listing of all Cultural Organizations in the Department of Cultural Affairs directory.
+		Cultural Org.~\cite{base:cultural} & Listing of all Cultural Organizations in the Department of Cultural Affairs directory.
 &    333,3kB    &        csv        \\ \midrule
-		     4      &       NYC Borough~\cite{base:borough}       & Polygon boundaries of boroughs (water areas excluded).
+		 NYC Borough~\cite{base:borough}   & Polygon boundaries of boroughs (water areas excluded).
 &    400,5kB    &      GeoJson      \\ \bottomrule
 	\end{tabular}
-\end{table*}
+\end{table}
 
-\vspace{-0.2cm}
-\subsection{Settings}
-
-In this step was used three different approaches to read the data (csv files): (i) SqlContext with databricks; (ii) parquet; and (iii) pandas.
-After, it was create a unique dataframe with the necessary informations.
-To help in the analsys, the Cultural Organizations and Incidents dataset received a score a they are like a column unique in the new dataframe.
-How we have 5 districts in New York, and to be easy, the Cultural Organizations and Incidents dataset were grouped and ranked in relation to the order (1-5), where 1 is the work and 5 the best.
-In this case, the datasets were ordered by the number in each district, ascendant for cultural organizations and descendant for the incidents.
-In the end, we have a unique dataset with 37043 rows.
+%\vspace{-0.2cm}
+%\subsection{Integration Data}
+%
+%To help in the analyses, the Cultural Organizations and Incidents dataset received a score.
+How we have 5 districts in New York, and to be easy, the Cultural Organizations and Incidents dataset were grouped and ranked in relation to the order (0-4), where 0 is the worst and 4 the best.
+In this case, the datasets were ordered by the number in each district, ascendant for Cultural Organizations and descendant for the Incidents.
+In the end, it was create a unique data frame with the necessary informations that contains 37043 rows.
 
@@
 
-\begin{figure}[!htpb]
-	\centering
-	\includegraphics[width=\linewidth]{images/price_per_district}
-	\caption{Mean Price per District}
-	\label{fig:casPf}
-\end{figure}
+This section shows and discusses the results in order to answer the researches questions.
+
+\subsection{Answering RQ1}
+
+Figure~\ref{fig:pairwiserelationsprincipalfeatures} shows, per district, a matrix of each feature as a function of another which is useful to check for any collinearity among the feature.
+The cells running through the diagonal of the matrix contain a histogram with its values on the X axis.
+The features chose to be analyzed were: price, cultural organizations and incidents.
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{images/cultural_organizations_per_district}
-	\caption{Number of Cultural Organizations per District}
-	\label{fig:eshopPf}
-\end{figure}
-
-\begin{figure}[!htpb]
-	\centering
-	\includegraphics[width=\linewidth]{images/incidents_per_district}
-	\caption{Number of Incidents per District}
-	\label{fig:jamesPf}
-\end{figure}
-
-\begin{figure}[!htpb]
-	\centering
-	\includegraphics[width=\linewidth]{images/pairwise_relations_principal_features}
+	\includegraphics[width=\linewidth]{images/related_data2}
 	\caption{}
@@
 
-\subsection{RQ1 - Comparing}
+%J: Old
+%Based on the figure, we do see that the results are loosely related and not resemblance of a straight line.
+Thus, there is no strong evidence of collinearity among the features.
+However, we can observe that Queens and Bronx are in the trade-off among the features.
+To help in to check this observation, Figure~\ref{fig:datadistribution} shows the data distribution in relation the listings mean price per district (Figure~\ref{fig:datadistribution:price}), the number of cultural organizations per district (Figure~\ref{fig:datadistribution:cultural}), and the number of incidents per district (Figure~\ref{fig:datadistribution:incidents}).
+We can observe in Figure~\ref{fig:datadistribution:price} that Manhattan district has the highest listings mean price, and Queens and Bronx are the lowest.
+In Figure~\ref{fig:datadistribution:cultural}, we can observe that Manhattan stands out followed by Brooklyn.
+On the other hand, Brooklyn stands out followed by Manhattan when we considers incidents (Figure~\ref{fig:datadistribution:incidents}).
+In this sense, we can to affirm that Queens and Bronx have the best trade-off among mean price, cultural organizations and incidents.
 
-\subsection{RQ2 - UCB}
+%J: Old
+%Based on the figure, we do see that the results are loosely related and not resemblance of a straight line.
+Thus, there is no strong evidence of collinearity among the features.
+However, we can observe that Queens and Bronx are in the trade-off among the features.
+To help in to check this observation, Figure~\ref{fig:datadistribution:price} shows that Manhattan district has the highest listings mean price, and Queens and Bronx are the lowest.
+In Figure~\ref{fig:datadistribution:cultural}, we can observe that Manhattan stands out followed by Brooklyn.
+On the other hand, Brooklyn stands out followed by Manhattan when we considers incidents (Figure~\ref{fig:datadistribution:incidents}).
+In this sense, we can to affirm that Queens and Bronx have the best trade-off among mean price, cultural organizations and incidents.
 
-\subsection{Threats To Validity}
-\label{sec:results:threats}
+Based on the figure, we do see that Queens and Bronx are in the trade-off among the features.
+To help in to check this observation, Figure~\ref{fig:datadistribution:price} shows that Manhattan district has the highest listings mean price, and Queens and Bronx are the lowest.
+In Figure~\ref{fig:datadistribution:cultural}, we can observe that Manhattan stands out followed by Brooklyn.
+On the other hand, Brooklyn stands out followed by Manhattan when we considers incidents (Figure~\ref{fig:datadistribution:incidents}).
+In this sense, we can to affirm that Queens and Bronx have the best trade-off among mean price, cultural organizations and incidents.
+
+\begin{figure}[!htpb]
+	\centering
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[scale=0.27]{images/price_per_district}
+		\caption{Mean Price per District}
+		\label{fig:datadistribution:price}
+	\end{subfigure}
+	\hfill	
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[scale=0.27]{images/cultural_organizations_per_district}
+		\caption{N. Cultural Organizations per District}
+		\label{fig:datadistribution:cultural}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[scale=0.27]{images/incidents_per_district}
+		\caption{N. Incidents per District}
+		\label{fig:datadistribution:incidents}
+	\end{subfigure}
+
+	\caption{Data Distribution per District}	
+	\label{fig:datadistribution}
+\end{figure}
+
+Figure~\ref{fig:meanpriceperaccomodate} shows mean price grouped by the number of people that can accommodate per district: Queens, Manhattan, Bronx, Brooklyn, and Staten Island.
+We can observe that Manhattan's district has more options than other ones.
+It's interesting highlight Queens district outperformed Bronx in the diversity of accommodates.
+
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=\linewidth]{images/mean_price_per_accomodate}
+	\caption{}
+	\label{fig:meanpriceperaccomodate}
+\end{figure}
+
+Analyzing the results, we can conclude that where it has more cultural organizations is more expensive and consequently attracts more incidents.
+However, we found two districts in the trade-off among price, cultural organizations and incidents: Queens and Bronx; where comparing these districts Queens outperforms Bronx in the diversity of accommodates.
+
+\subsection{Answering RQ2}
+
+For this analysis using machine learning we split our dataset into a train and test (80/20).
+We run 7 regression models to calculate the Train and Test Score: Linear Regression, Ridge Regression, Lasso Regression, Elastic Net, Bayes Ridge Regression, Orthogonal Matching Pursuit (OMP), and Gradient Boosting Regressor (GBR).
+In the analysis, we used 6 regression models and compared with GBR using an exhaustive "grid search" which simply tries all the supplied parameter combinations and uses cross-validation folding to find the best one.
+
+Figure~\ref{fig:medianabsoluteerrorprice} shows the Linear Regression, Ridge Regression, Lasso Regression, Elastic Net, Bayes Ridge Regression, OMP and their Median Absolute Error.
+Intuitively, Median Absolute Error is less sensitive to outliers than Mean Squared Error and translates nicely to a dollar amount that is relative to price.
+
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=\linewidth]{images/median_absolute_error_price}
+	\caption{Price - Median Absolute Error}
+	\label{fig:medianabsoluteerrorprice}
+\end{figure}
+
+When analyzing these six estimators by their Median Absolute Error, we see that they appear to be roughly the same with most of the estimators being able to predict the price with a median error around 30-35 dollars, with Lasso regression outperforms other ones with small margin and a Median Absolute Error of \$34.59.
+
+We next fit an ensemble method, GBR, and compare its results to that of our previous models.
+We run it for 300 iterations and the result is a Median Absolute Error of \$23.91, approximately 31\% less than Lasso Regression.
+We see that GBR, in regards to Median Absolute Error, outperforms Lasso Regression.
+
+%Figure~\ref{fig:gradientboostingregressorprice} shows how the error is affected by each round of boosting.
+
+%\begin{figure}[!htpb]
+%		\centering
+%		\includegraphics[width=\linewidth]{images/gradient_boosting_regressor_price}
+%		\caption{Gradient Boosting Regressor - Error values affected by each round of boosting}
+%		\label{fig:gradientboostingregressorprice}
+%\end{figure}
+
+%We can observe in Figure~\ref{fig:gradientboostingregressorprice} that the graph begins to converge between 150 and 200 iterations, but is still benefiting from more iterations, so we could increase the iterations to increase the results.
+
+After, we calculate the feature importances to see which features were most influential in predicting the listing price, Figure~\ref{fig:featureimportanc_gridSearchCVprice}.
+This show a relative scoring of how important each feature is relative to the feature with the most importance.
+
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=\linewidth]{images/feature_importance_gridSearchCV_price}
+	\caption{Gradient Boosting Regressor - Feature Importance}
+	\label{fig:featureimportanc_gridSearchCVprice}
+\end{figure}
+
+Clearly some of the variables have more influence than others, and the most influential feature is the ``Entire home/apt'' attribute; this indicates whether or not the unit is shared with other people, and has the most effect in setting the price.
+This feature is followed by accommodates, cultural organizations and Manhattan district, and the feature incidents was not so influent.
+In this sense, we can conclude that the local is not so influent in to predict the price, but the room type.
+
+\section{Problems found}
+\label{sec:problemsfound}
+
+We identified some points that can be problems found during the work: (i) The listings data set had problem to read it and a workaround was done using R language; (ii) Organizing the data to create a possible research question and answer it; and (iii) How to use machine learning to show something that could not be answered, i.
+e., using charts, maps or display the raw data in the DataFrame provided by Apache Spark.
 
@@
 \label{sec:conclusion}
+
+This work introduces an analysis trying to discovery if the cultural organizations and incidents influence on listing price.
+The ideia is to check the collinearity the features, try to predict the price using regression models, and to check the level importance of the features chose.
+
+We implemented and evaluated the New York City in relation the Airbnb listings.
+The results shows that where it has more cultural organization it has more incidents probability.
+Besides, the cultural organization was the third feature more influent in to predict the price.
+Using Gradient Boosting Regression we were able to fit a model that obtained a Median Absolute Error of \$23.91 for all listing data.
+
+For a practical predictor to be used in practice, future work will need to be done to further explore and build more suitable models.
+Predicting a significantly skewed right response variable, price, yields a set of challenges that need to be addressed rather than predicting a specific price.
+Future works could consider population density, property price, and an analysis by neighborhood.
 

### 2017-05-05 article/main.tex
step 5

@@
 \begin{abstract}
-	Airbnb is an outstanding hosting service used worldwide and provides information to its users in a simple and efficient manner, although this information is limited only to listings of its products.
+	Airbnb is an outstanding hosting service used worldwide and provides information to its users in a simple and efficient manner.
 In this work, an analysis is made taking into account if incidents and cultural organizations influence the prices practiced in Airbnb.
-Besides, the prediction of new prices is carried out that the user can come to inform taking into account information of the current listings.
-The price forecast has some advantages when advising the user: on the price practiced (is too large or small), the mode of advertisement, or even on the investment decisions of the market analysis.
-To help in this task, the present work performs an analysis using graphs, maps and different types of machine learning.
-The data reveals that Queens district has the more adequate trade-off among price, cultural organization, and incidents as well as the accommodates diversity.
-Besides, cultural organization has a high influence in to predict price.
+To help in this task, the present work performs an analysis using charts, maps and different types of machine learning.
+The data reveals that Queens district has a fair trade-off among price, cultural organization, and incidents, as well as, the accommodates diversity.
+Besides, the cultural organization has a high influence in to predict price.
 \end{abstract}
@@
 
-Airbnb was founded in August of 2008 and based in San Francisco, California.
+%Airbnb was founded in August of 2008 and based in San Francisco, California.
 Airbnb is an online marketplace and hospitality service, enabling people to lease or rent short-term lodging including vacation rentals, apartment rentals, homestays, hostel beds, or hotel rooms.
 
-%The company does not own any lodging; it is merely a broker and receives percentage service fees (commissions) from both guests and hosts in conjunction with every booking.
-It has over 3,000,000 lodging listings in 65,000 cities and 191 countries, and the host sets the cost of accommodation.
-Like all hospitality services, Airbnb is a form of collaborative consumption and sharing.
-Airbnb has two million rooms available - nearly three times more than that of the largest hotel chain in the world.
-
-Airbnb has help a lot of people, but how can we predict a price or if the cultural organizations and incidents impacts on listing price?
-In some moments, the guests want to a local cheap or more attractive considering local events to appreciate.
-Thus, predicting a cheap and safe local is arguably important.
-In this paper, we try and capture this characteristic using maps, charts and machine learning to help the guest in the chose.
+In some moments, the guests want to a local to be cheaper or more attractive considering local events to appreciate, besides a safe local is arguably necessary.
+Considering the Airbnb listing from New York City (NYC), how the cultural organizations and incidents impacts on listing price?
 
@@
 Section~\ref{sec:results} presents and analyses the results obtained.
+Section~\ref{sec:problemsfound}, describes the problems found during the work.
 Finally, Section~\ref{sec:conclusion} concludes the paper and discusses the future work.
@@
 
-The hypothesis of this work\footnote{The project is available at https://github.com/jacksonpradolima/airbnb-ny-analysis} is that our approach is capable to recommend a cheap and safe local (district/borough) as well as consider the influence of these aspect in to predict listing price.
-To evaluate this, we consider uses maps, charts and machine learning.
+The hypothesis of this work\footnote{The project is available at https://github.com/jacksonpradolima/airbnb-ny-analysis} is that our approach is capable of found the influence of cultural organizations and incidents in to predict listing price as well as recommending a cheap and safe local (district/borough).
 
-According to our goals the experiment was guided by the following researches questions: \textbf{RQ1:} ``How the incidents and cultural organizations impact on listing price?'' and \textbf{RQ2:} ``How the incidents and cultural organizations impact on regression model to predict the listing price?''.
+According to our goals the experiment was guided by the following research question: ``How the incidents and cultural organizations impact on listing price?''.
 
-To answer the RQ1 we compared the result shows on maps, a collinearity matrix among the features, and how the accommodates are distributed.
-To answer the RQ2 we used a machine learning with 7 regression models and the results were compared using Median Absolute Error.
+To answer the research question, we compared the result shows on maps, a collinearity matrix among the features, and how the accommodates are distributed.
+Additionally, we used a machine learning with seven regression models, and the results were compared using Median Absolute Error.
+Besides, two algorithms for classification were used to see the difficult to predict the most influent features.
 
@@
 
-The investigation focused on four dataset collected in open data sites.
-These dataset are as follows: 1) Listings, a dataset that is a Airbnb snapshot of 02 April, 2017; 2) Incidents, contains all incidents from New York for the year 2016; 3) Cultural Organizations, contains all cultural organizations from New York in 2017; and 4) NYC Borough, contains informations about boundaries of boroughs (districts).
-Further information about these datasets are available in the Table~\ref{tab:datasets}.
+The investigation focused on four datasets collected in open data sites.
+These datasets are as follows: 1) Listings, a dataset that is an Airbnb snapshot of 02 April 2017 from NYC; 2) Incidents, contains all incidents from NYC for the year 2016; 3) Cultural Organizations, contains all cultural organizations from NYC in 2017; and 4) NYC Borough, contains information about boundaries of boroughs (districts).
+Further information about these datasets is available in Table~\ref{tab:datasets}.
 
@@
 	\centering
-	\caption{Data sets used in the experiment.}
+	\caption{Data sets used in the experiment}
 	\label{tab:datasets}
@@
 		\toprule
-		         \textbf{Dataset}          & \textbf{Description}                                                                                                                          & \textbf{Size} & \textbf{Download} \\ \midrule
+		         \textbf{Dataset}          & \textbf{Description}                                                                                                                   & \textbf{Size} & \textbf{Format} \\ \midrule
 		   Listings~\cite{base:airbnb}     & Detailed listings data, including various attributes (features) of each listing such as number of bedrooms, bathrooms, location, etc.
 &    153,7MB    &       csv       \\ \midrule
-		 Incidents~\cite{base:incidents}   & All valid felony, misdemeanor, and violation crimes reported to the New York City Police Department (NYPD) for all complete quarters in 2016.
+		 Incidents~\cite{base:incidents}   & All valid felony, misdemeanor, and violation crimes reported to the New York City Police Department for all complete quarters in 2016.
 &    124,2MB    &       csv       \\ \midrule
@@
 
-This section shows and discusses the results in order to answer the researches questions.
+This section shows and discusses the results to answer the research question.
 
-\subsection{Answering RQ1}
-
-Figure~\ref{fig:pairwiserelationsprincipalfeatures} shows, per district, a matrix of each feature as a function of another which is useful to check for any collinearity among the feature.
+Figure~\ref{fig:pairwiserelationsprincipalfeatures} shows, per district, a matrix of each feature as a function of another which is useful to check for any collinearity among the features.
 The cells running through the diagonal of the matrix contain a histogram with its values on the X axis.
-The features chose to be analyzed were: price, cultural organizations and incidents.
+The features chose to be analyzed were: price, cultural organizations, and incidents.
 
@@
 	\includegraphics[width=\linewidth]{images/related_data2}
-	\caption{}
+	\caption{Collinearity Among the Features}
 	\label{fig:pairwiserelationsprincipalfeatures}
@@
 In Figure~\ref{fig:datadistribution:cultural}, we can observe that Manhattan stands out followed by Brooklyn.
-On the other hand, Brooklyn stands out followed by Manhattan when we considers incidents (Figure~\ref{fig:datadistribution:incidents}).
-In this sense, we can to affirm that Queens and Bronx have the best trade-off among mean price, cultural organizations and incidents.
+On the other hand, Brooklyn stands out followed by Manhattan when we consider incidents (Figure~\ref{fig:datadistribution:incidents}).
+In this sense, we can affirm that Queens and Bronx have the best trade-off among mean price, cultural organizations and incidents.
+
+%\begin{figure}[!htpb]
+%	\centering
+%	\begin{subfigure}{0.5\textwidth}
+%		\centering
+%		\includegraphics[scale=0.27]{images/price_per_district}
+%		\caption{Mean Price per District}
+%		\label{fig:datadistribution:price}
+%	\end{subfigure}
+%	\hfill	
+%	\begin{subfigure}{0.5\textwidth}
+%		\centering
+%		\includegraphics[scale=0.27]{images/cultural_organizations_per_district}
+%		\caption{N. Cultural Organizations per District}
+%		\label{fig:datadistribution:cultural}
+%	\end{subfigure}
+%	\hfill
+%	\begin{subfigure}{0.5\textwidth}
+%		\centering
+%		\includegraphics[scale=0.27]{images/incidents_per_district}
+%		\caption{N. Incidents per District}
+%		\label{fig:datadistribution:incidents}
+%	\end{subfigure}
+%	
+%	\caption{Data Distribution per District}	
+%	\label{fig:datadistribution}
+%\end{figure}
 
@@
 	\centering
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[scale=0.27]{images/price_per_district}
-		\caption{Mean Price per District}
+	\includegraphics[width=0.7\linewidth]{images/price_per_district}
+	\caption{Collinearity Among the Features}
 	\label{fig:datadistribution:price}
-	\end{subfigure}
-	\hfill	
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[scale=0.27]{images/cultural_organizations_per_district}
-		\caption{N. Cultural Organizations per District}
-		\label{fig:datadistribution:cultural}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[scale=0.27]{images/incidents_per_district}
-		\caption{N. Incidents per District}
-		\label{fig:datadistribution:incidents}
-	\end{subfigure}
-
-	\caption{Data Distribution per District}	
-	\label{fig:datadistribution}
 \end{figure}
 
-Figure~\ref{fig:meanpriceperaccomodate} shows mean price grouped by the number of people that can accommodate per district: Queens, Manhattan, Bronx, Brooklyn, and Staten Island.
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=0.7\linewidth]{images/cultural_organizations_per_district}
+	\caption{Collinearity Among the Features}
+	\label{fig:datadistribution:cultural}
+\end{figure}
+
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=0.7\linewidth]{images/incidents_per_district}
+	\caption{Collinearity Among the Features}
+	\label{fig:datadistribution:incidents}
+\end{figure}
+
+Figure~\ref{fig:meanpriceperaccomodate} shows mean price grouped by the number of people that can be accommodated (number of beds)  with a limited of four accommodates, when we can begin see differences, per district: Queens, Manhattan, Bronx, Brooklyn, and Staten Island.
 We can observe that Manhattan's district has more options than other ones.
-It's interesting highlight Queens district outperformed Bronx in the diversity of accommodates.
+It's interesting to highlight Queens district outperformed the Bronx in the diversity of accommodates.
 
@@
 	\includegraphics[width=\linewidth]{images/mean_price_per_accomodate}
-	\caption{}
+	\caption{Mean price grouped by the number of people that can accommodate}
 	\label{fig:meanpriceperaccomodate}
@@
 
-Analyzing the results, we can conclude that where it has more cultural organizations is more expensive and consequently attracts more incidents.
-However, we found two districts in the trade-off among price, cultural organizations and incidents: Queens and Bronx; where comparing these districts Queens outperforms Bronx in the diversity of accommodates.
+Next, we used machine learning and for this we split our dataset into an 80\% train and 20\% test.
+In this step, we run seven regression models: Linear Regression, Ridge Regression, Lasso Regression, Elastic Net, Bayes Ridge Regression, Orthogonal Matching Pursuit (OMP), and Gradient Boosting Regressor (GBR); and two algorithms for classification: Decision Tree and Random Forest.
+First, we compared the regression models, where GBR was tunned with 300 iterations and used an exhaustive "grid search" which only tries all the supplied parameter combinations and uses cross-validation folding to find the best one.
 
-\subsection{Answering RQ2}
-
-For this analysis using machine learning we split our dataset into a train and test (80/20).
-We run 7 regression models to calculate the Train and Test Score: Linear Regression, Ridge Regression, Lasso Regression, Elastic Net, Bayes Ridge Regression, Orthogonal Matching Pursuit (OMP), and Gradient Boosting Regressor (GBR).
-In the analysis, we used 6 regression models and compared with GBR using an exhaustive "grid search" which simply tries all the supplied parameter combinations and uses cross-validation folding to find the best one.
-
-Figure~\ref{fig:medianabsoluteerrorprice} shows the Linear Regression, Ridge Regression, Lasso Regression, Elastic Net, Bayes Ridge Regression, OMP and their Median Absolute Error.
-Intuitively, Median Absolute Error is less sensitive to outliers than Mean Squared Error and translates nicely to a dollar amount that is relative to price.
+Figure~\ref{fig:medianabsoluteerrorprice} shows the regression models their Median Absolute Error.
+Intuitively, Median Absolute Error is less sensitive to outliers than Mean Squared Error and translates nicely to a dollar amount that is about price.
 
@@
 
-When analyzing these six estimators by their Median Absolute Error, we see that they appear to be roughly the same with most of the estimators being able to predict the price with a median error around 30-35 dollars, with Lasso regression outperforms other ones with small margin and a Median Absolute Error of \$34.59.
-
-We next fit an ensemble method, GBR, and compare its results to that of our previous models.
-We run it for 300 iterations and the result is a Median Absolute Error of \$23.91, approximately 31\% less than Lasso Regression.
-We see that GBR, in regards to Median Absolute Error, outperforms Lasso Regression.
+When analyzing these estimators by their Median Absolute Error, we see that GBR outperforms the other ones with a Median Absolute Error of \$23.86, approximately 31\% less than Lasso Regression that appear in second with a Median Absolute Error of \$34.59.
 
@@
 After, we calculate the feature importances to see which features were most influential in predicting the listing price, Figure~\ref{fig:featureimportanc_gridSearchCVprice}.
-This show a relative scoring of how important each feature is relative to the feature with the most importance.
+This show a relative scoring of how important each feature is about the feature with the most importance.
 
@@
 
-Clearly some of the variables have more influence than others, and the most influential feature is the ``Entire home/apt'' attribute; this indicates whether or not the unit is shared with other people, and has the most effect in setting the price.
-This feature is followed by accommodates, cultural organizations and Manhattan district, and the feature incidents was not so influent.
-In this sense, we can conclude that the local is not so influent in to predict the price, but the room type.
+Clearly, some of the variables have more influence than others, and the most important feature is the ``Entire home/apt'' attribute; this indicates whether or not the unit is shared with other people, and has the most effect in setting the price.
+This feature is followed by accommodates, cultural organizations and Manhattan district, and the feature incidents were not so influent.
 
-\section{Problems found}
+In the last, we tried to predict the three most influent features using algorithms for classification. Table~\ref{tab:classification} shows in bold the best test error values.
+
+\begin{table}[!htpb]
+	\fontsize{7pt}{7pt}\selectfont
+	\centering
+	\caption{Classification by Feature Importance}
+	\label{tab:classification}
+	\begin{tabular}{ccc}
+		\toprule
+		   \textbf{Feature}    & \textbf{Decision Tree} & \textbf{Random Forest} \\ \midrule
+		   Entire home/apt     &    \textbf{0.0000}     &         0.0009         \\ \midrule
+		     Accommodates      &    \textbf{0.4115}     &         0.4151         \\ \midrule
+		Cultural Organizations &    \textbf{0.0000}     &    \textbf{0.0000}     \\ \bottomrule
+	\end{tabular}
+\end{table}
+
+Analyzing the results, we found two districts in the trade-off among price, cultural organizations and incidents: Queens and Bronx; where comparing these districts Queens outperform the Bronx in the diversity of accommodates.
+In relation the regression models, we can conclude that the local is not so influent in to predict the price, but the room type.
+In relation the algorithms for classification, the Decision Tree outperforms Random Forest and the feature with more difficult to predict was ``Accommodates''.
+Besides, the cultural organizations have a strong relation with the data where there was not test error.
+Thus, we can conclude that cultural organization has a strong influence on listing price and where there are more cultural organizations is more expensive and consequently attracts more incidents.
+
+\section{Problems Found}
 \label{sec:problemsfound}
 
-We identified some points that can be problems found during the work: (i) The listings data set had problem to read it and a workaround was done using R language; (ii) Organizing the data to create a possible research question and answer it; and (iii) How to use machine learning to show something that could not be answered, i.
-e., using charts, maps or display the raw data in the DataFrame provided by Apache Spark.
+We identified some points that can be problems found during the work: (i) The listings data set had problem to read it, and a workaround was done using R language; (ii) The Apache Spark regression evaluator has not the median absolute error metric, for this reason it was used sci-kit learn library.
 
@@
 
-This work introduces an analysis trying to discovery if the cultural organizations and incidents influence on listing price.
-The ideia is to check the collinearity the features, try to predict the price using regression models, and to check the level importance of the features chose.
+This work introduces an analysis trying to discover if the cultural organizations and incidents influence on listing price.
+The idea is to check the collinearity the features, try to predict the price using regression models, verify the level importance of the features chose and classify them using algorithms for classification.
 
-We implemented and evaluated the New York City in relation the Airbnb listings.
-The results shows that where it has more cultural organization it has more incidents probability.
-Besides, the cultural organization was the third feature more influent in to predict the price.
-Using Gradient Boosting Regression we were able to fit a model that obtained a Median Absolute Error of \$23.91 for all listing data.
+We implemented and evaluated the New York City in relation with the Airbnb listings.
+The results show that where it has a more cultural organization, it has more incidents probability.
+Using Gradient Boosting Regression, we were able to fit a model that obtained a Median Absolute Error of \$23.91 for all listing data.
+Besides, the cultural organization was the third feature more influent in the prediction of the price.
+In relation the classification using Decision Tree, we were able to classify the features with the minimum test error.
 
-For a practical predictor to be used in practice, future work will need to be done to further explore and build more suitable models.
-Predicting a significantly skewed right response variable, price, yields a set of challenges that need to be addressed rather than predicting a specific price.
-Future works could consider population density, property price, and an analysis by neighborhood.
+For a possible predictor to be used in practice, future work will need to be done to explore further and build more suitable models.
+Predicting a significantly skewed right response variable, price, yields a set of challenges that need to be addressed rather than predicting a particular price.
+Future works could consider population density, property price, and analysis by neighborhood.
 

### 2017-05-05 article/main.tex
finished article

@@
 	Airbnb is an outstanding hosting service used worldwide and provides information to its users in a simple and efficient manner.
-In this work, an analysis is made taking into account if incidents and cultural organizations influence the prices practiced in Airbnb.
-To help in this task, the present work performs an analysis using charts, maps and different types of machine learning.
+In this study, an analysis is made taking into account if incidents and cultural organizations influence the prices practiced in Airbnb.
+To help in this task, the present study performs an analysis using charts, maps and different types of machine learning.
 The data reveals that Queens district has a fair trade-off among price, cultural organization, and incidents, as well as, the accommodates diversity.
-Besides, the cultural organization has a high influence in to predict price.
+Besides, the cultural organization has a high influence in the price prediction.
 \end{abstract}
@@
 Section~\ref{sec:results} presents and analyses the results obtained.
-Section~\ref{sec:problemsfound}, describes the problems found during the work.
+Section~\ref{sec:problemsfound}, describes the problems found during the study.
 Finally, Section~\ref{sec:conclusion} concludes the paper and discusses the future work.
@@
 
-The hypothesis of this work\footnote{The project is available at https://github.com/jacksonpradolima/airbnb-ny-analysis} is that our approach is capable of found the influence of cultural organizations and incidents in to predict listing price as well as recommending a cheap and safe local (district/borough).
+The hypothesis of this study\footnote{The project is available at https://github.com/jacksonpradolima/airbnb-ny-analysis} is that our approach is able to find the influence of cultural organizations and incidents in to predict listing price as well as recommending a cheap and safe local (district/borough).
 
@@
 
-To answer the research question, we compared the result shows on maps, a collinearity matrix among the features, and how the accommodates are distributed.
+To answer the research question, we compared the result showed on maps, a collinearity matrix among the features, and how the accommodates are distributed.
 Additionally, we used a machine learning with seven regression models, and the results were compared using Median Absolute Error.
@@
 
-The investigation focused on four datasets collected in open data sites.
-These datasets are as follows: 1) Listings, a dataset that is an Airbnb snapshot of 02 April 2017 from NYC; 2) Incidents, contains all incidents from NYC for the year 2016; 3) Cultural Organizations, contains all cultural organizations from NYC in 2017; and 4) NYC Borough, contains information about boundaries of boroughs (districts).
+The investigation focused on four datasets collected in open data sites: 1) Listings; 2) Incidents; 3) Cultural Organizations; and 4) NYC Borough.
 Further information about these datasets is available in Table~\ref{tab:datasets}.
@@
 &    124,2MB    &       csv       \\ \midrule
-		Cultural Org.~\cite{base:cultural} & Listing of all Cultural Organizations in the Department of Cultural Affairs directory.
+		Cultural Org.~\cite{base:cultural} & Listing of all Cultural Organizations in the Department of Cultural Affairs directory (2017).
 &    333,3kB    &       csv       \\ \midrule
@@
 %
-%To help in the analyses, the Cultural Organizations and Incidents dataset received a score.
-How we have 5 districts in New York, and to be easy, the Cultural Organizations and Incidents dataset were grouped and ranked in relation to the order (0-4), where 0 is the worst and 4 the best.
+To help in the analyses, the Cultural Organizations and Incidents dataset received a score.
+Since we have 5 districts in New York, and to simplify, the Cultural Organizations and Incidents dataset were grouped and ranked in relation to the order (1-5), where 1 is the worst and 5 the best.
 In this case, the datasets were ordered by the number in each district, ascendant for Cultural Organizations and descendant for the Incidents.
@@
 The cells running through the diagonal of the matrix contain a histogram with its values on the X axis.
-The features chose to be analyzed were: price, cultural organizations, and incidents.
+The features chosen to be analyzed were: price, cultural organizations, and incidents.
 
@@
 Based on the figure, we do see that Queens and Bronx are in the trade-off among the features.
-To help in to check this observation, Figure~\ref{fig:datadistribution:price} shows that Manhattan district has the highest listings mean price, and Queens and Bronx are the lowest.
+To help checking this observation, Figure~\ref{fig:datadistribution:price} shows that Manhattan district has the highest listings mean price, and Queens and Bronx are the lowest.
 In Figure~\ref{fig:datadistribution:cultural}, we can observe that Manhattan stands out followed by Brooklyn.
@@
 In this sense, we can affirm that Queens and Bronx have the best trade-off among mean price, cultural organizations and incidents.
+Besides, the price is more distributed in highest cultural organizations scores and in the lowest incidents score, where we can see that these features are correlated.
 
@@
 
-Figure~\ref{fig:meanpriceperaccomodate} shows mean price grouped by the number of people that can be accommodated (number of beds)  with a limited of four accommodates, when we can begin see differences, per district: Queens, Manhattan, Bronx, Brooklyn, and Staten Island.
+Figure~\ref{fig:meanpriceperaccomodate} shows mean price grouped by the number of people that can be accommodated (number of beds) with a limited of four accommodates, price less than \$1000 and a minimum of 50 listings, when we can begin see differences for a cheap local with diversity, per district: Queens, Manhattan, Bronx, Brooklyn, and Staten Island.
 We can observe that Manhattan's district has more options than other ones.
@@
 
-Next, we used machine learning and for this we split our dataset into an 80\% train and 20\% test.
-In this step, we run seven regression models: Linear Regression, Ridge Regression, Lasso Regression, Elastic Net, Bayes Ridge Regression, Orthogonal Matching Pursuit (OMP), and Gradient Boosting Regressor (GBR); and two algorithms for classification: Decision Tree and Random Forest.
+Next, we used machine learning and for this we split our dataset into an 80\% train and 20\% test and the informations chosen from the dataset were:  \textit{price}, \textit{accommodates}, \textit{bedrooms}, \textit{beds}, \textit{district}, \textit{room type}, \textit{cancellation policy}, \textit{instant bookable}, \textit{reviews per month}, \textit{number of reviews}, \textit{availability 30} and \textit{review scores rating}.
+In the case of the columns that contain categorical variables these were handled in slightly different ways depending on their possible values and these values were transformed into new columns.
+
+We run seven regression models: Linear Regression, Ridge Regression, Lasso Regression, Elastic Net, Bayes Ridge Regression, Orthogonal Matching Pursuit (OMP), and Gradient Boosting Regressor (GBR); and two algorithms for classification: Decision Tree and Random Forest.
 First, we compared the regression models, where GBR was tunned with 300 iterations and used an exhaustive "grid search" which only tries all the supplied parameter combinations and uses cross-validation folding to find the best one.
 
-Figure~\ref{fig:medianabsoluteerrorprice} shows the regression models their Median Absolute Error.
+Figure~\ref{fig:medianabsoluteerrorprice} shows the regression models by their Median Absolute Error.
 Intuitively, Median Absolute Error is less sensitive to outliers than Mean Squared Error and translates nicely to a dollar amount that is about price.
@@
 	\centering
-	\includegraphics[width=\linewidth]{images/median_absolute_error_price}
+	\includegraphics[width=0.8\linewidth]{images/median_absolute_error_price}
 	\caption{Price - Median Absolute Error}
@@
 When analyzing these estimators by their Median Absolute Error, we see that GBR outperforms the other ones with a Median Absolute Error of \$23.86, approximately 31\% less than Lasso Regression that appear in second with a Median Absolute Error of \$34.59.
-
-%Figure~\ref{fig:gradientboostingregressorprice} shows how the error is affected by each round of boosting.
-
-%\begin{figure}[!htpb]
-%		\centering
-%		\includegraphics[width=\linewidth]{images/gradient_boosting_regressor_price}
-%		\caption{Gradient Boosting Regressor - Error values affected by each round of boosting}
-%		\label{fig:gradientboostingregressorprice}
-%\end{figure}
-
-%We can observe in Figure~\ref{fig:gradientboostingregressorprice} that the graph begins to converge between 150 and 200 iterations, but is still benefiting from more iterations, so we could increase the iterations to increase the results.
-
-After, we calculate the feature importances to see which features were most influential in predicting the listing price, Figure~\ref{fig:featureimportanc_gridSearchCVprice}.
+Then, we calculate the feature importances to see which features were most influential in predicting the listing price, Figure~\ref{fig:featureimportanc_gridSearchCVprice}.
 This show a relative scoring of how important each feature is about the feature with the most importance.
@@
 	\centering
-	\includegraphics[width=\linewidth]{images/feature_importance_gridSearchCV_price}
+	\includegraphics[width=0.9\linewidth]{images/feature_importance_gridSearchCV_price}
 	\caption{Gradient Boosting Regressor - Feature Importance}
@@
 
-Clearly, some of the variables have more influence than others, and the most important feature is the ``Entire home/apt'' attribute; this indicates whether or not the unit is shared with other people, and has the most effect in setting the price.
+Clearly, some of the variables have more influence than others, and the most important feature is the \textit{Entire home/apt} attribute; this indicates whether or not the unit is shared with other people, and has the most effect in setting the price.
 This feature is followed by accommodates, cultural organizations and Manhattan district, and the feature incidents were not so influent.
 
-In the last, we tried to predict the three most influent features using algorithms for classification. Table~\ref{tab:classification} shows in bold the best test error values.
+By last, we tried to predict each one the three most influent features for the GBR model, Figure~\ref{fig:featureimportanc_gridSearchCVprice}, using algorithms for classification.
+Table~\ref{tab:classification} shows in bold the best test error values.
+The Decision Tree outperforms Random Forest and the feature with more difficult to predict was \textit{accommodates}.
 
@@
 
-Analyzing the results, we found two districts in the trade-off among price, cultural organizations and incidents: Queens and Bronx; where comparing these districts Queens outperform the Bronx in the diversity of accommodates.
-In relation the regression models, we can conclude that the local is not so influent in to predict the price, but the room type.
-In relation the algorithms for classification, the Decision Tree outperforms Random Forest and the feature with more difficult to predict was ``Accommodates''.
-Besides, the cultural organizations have a strong relation with the data where there was not test error.
+In summary, analyzing the results, we found two districts in the trade-off among price, cultural organizations and incidents: Queens and Bronx; when comparing these districts, Queens outperformed the Bronx in the diversity of accommodates.
+In relation to the machine learning, we can conclude that the local is not so influent in to predict the price, but the room type.
+Besides, the cultural organizations have a strong relation with the data.
 Thus, we can conclude that cultural organization has a strong influence on listing price and where there are more cultural organizations is more expensive and consequently attracts more incidents.
@@
 
-We identified some points that can be problems found during the work: (i) The listings data set had problem to read it, and a workaround was done using R language; (ii) The Apache Spark regression evaluator has not the median absolute error metric, for this reason it was used sci-kit learn library.
+We identified some points that can be problems found during the study: (i) The listings data set had problem to read it, and a workaround was done using R language; (ii) The Apache Spark regression evaluator has not the median absolute error metric, for this reason it was used sci-kit learn library.
 
@@
 
-This work introduces an analysis trying to discover if the cultural organizations and incidents influence on listing price.
-The idea is to check the collinearity the features, try to predict the price using regression models, verify the level importance of the features chose and classify them using algorithms for classification.
+This study introduces an analysis trying to discover if the cultural organizations and incidents influence on listing price.
+The idea is to check the collinearity of the features, try to predict the price using regression models, verify the level importance of the features chose and classify them using algorithms for classification.
 
